### 2016-04-13 ms/ms_probaweb.tex
Edits to the intro and model section

Biogeography has historically focused on the spatial distribution and
abundance of species, neglecting variation in the way species interact with
each other. Models of species distribution and of interactions have
historically taken different paths. Here, we plea for an integrated approach,
adopting the view that community structure is best represented as an
ecological network of interactions. We outline a conceptual approach,
suggesting that the ecological niche may be redefined to encompass the effect
of the environment on species distribution (the Grinnellian dimension of the
niche) and on the ecological interactions among them (the Eltonian dimension).
Starting from this novel concept, we develop a quantitative theory to explain
turnover of interactions in space and time – i.e. a novel approach to
interaction distribution modelling. We apply this framework to a large
data set of host–parasite interactions across Europe and find that two aspects
of the environment (temperature and precipitation) leave a strong imprint on
species co-occurrence, but not on the probability of local interactions. Even
where species co-occur, interaction proves a stochastic rather than
deterministic process, adding to variation in realized network structure. We
also find that a large majority of species pairs are never found together,
thus precluding any inferences regarding their probability to interact. Our
framework provides a first conceptual framework to explain the variation of
network structure at large spatial scales and opens new perspectives at the
frontier between species distribution modelling and community ecology.

@@

Community ecology is defined in most textbooks as \textit{the study of the
interactions that determine the distribution and abundance of organisms}
\citep{Krebs2001}. Despite a general consensus on this definition
(Scheiner2007), research on variation in community
structure has mostly focused on the spatial and temporal turnover of species composition
\citep{Anderson2011}, neglecting variation in the way species interact with
each other \citep{Poisot2015a}. Given this omission, it is perhaps not
surprising that biogeographers are still struggling to establish whether
interactions actually impact the distribution of species at large spatial
scales\citep{Wisz2012, Kissling2012}, even though there is enough evidence
from community ecology that interactions are critical for determining species
dynamics, resource use and responses to the environment af finer scales.
Recent attempts at accounting for interactions in species distribution models
\citep{Pollock2014, Pelissier2013} have brought some methodological advances.
Yet, these techniques are still based on a `species-based' approach to
communities, where interactions are merely treated as fixed covariates
affecting distribution.

As a more explicit description of interactions among species, the
network approach offers a convenient representation of communities. Species
are represented as nodes and interactions by links. To date, studies of
network diversity have mostly been concerned with the distribution of
interactions within locations, and less so with the variation among locations
\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is, however, 
ample evidence that interaction networks vary in space and time
\citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
theory provides an explanation for the variation in the distribution of the
different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
to the joint variation of node and link occurrences. Consequently, we urgently need a
conceptual framework to formalize these observations.

@@

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|\mathbf{T},X_{iy},X_{jy},E_y)
\end{equation}
%-----------------

The first term on the right-hand side of the equation is the probability of
observing the two species co-occurring at location $y$. It corresponds to the
Grinnellian dimension of the niche. The second term represents the probability
that an interaction occurs between species $i$ and $j$, given their set of
traits $T$ and that they are co-occurring. Above, we referred to this entity
as the ``metaweb'' and it corresponds to the Eltonian dimension of the niche. Below,
we will see how this formalism can be directly fit to empirical data. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms.

>>>>

Biogeography has historically focused on the spatial distribution and abundance
of species. Both are driven by the way species interact with one another,
but also by the way these interactions vary across time and space. Here,
we call for an integrated approach in which community structure represented
as a network of ecological interactions, and show how it translates to
biogeography questions. Under this representation, the niche is intergratively
defined to be both the effect of the environment on species distribution (the
Grinnellian dimension of the niche) and on the ecological interactions among
them (the Eltonian dimension). Starting from this novel concept, we develop a
quantitative theory to explain turnover of interactions in space and time -–
\emph{i.e.} a novel approach to interaction distribution modelling. We apply
this framework to host–parasite interactions across Europe and find that
two aspects of the environment (temperature and precipitation) leave a strong
imprint on species co-occurrence, but not on species interactions. Even where
species co-occur, interaction proves a stochastic rather than deterministic
process, adding to variation in realized network structure. We also find
that a large majority of species pairs are never found together, thus
precluding any inferences regarding their probability to interact. Our
framework provides a basis to explain the variation of network structure
at large spatial scales and opens new perspectives at the frontier between
species distribution modelling and community ecology.

@@

Community ecology is \textit{the study of the interactions that determine
the distribution and abundance of organisms} \citep{Krebs2001}. Despite a
general consensus on this definition (Scheiner2007), research on variation in
community structure has mostly focused on the spatial and temporal turnover
of species composition \citep{Anderson2011}, neglecting variation in the way
species interact with each other, despite accumulating empirical evidence that
this is a major source of diversity \citep{Poisot2015a}. Given this omission,
it is perhaps not surprising that biogeographers are still struggling to
establish whether interactions actually impact the distribution of species at
large spatial scales \citep{Wisz2012, Kissling2012}: treating interactions
as fixed events neglects a large part of the complexity of empirical
communities, and will most likely deliver underwhelming results. Recent
attempts at accounting for interactions in species distribution models
\citep{Pollock2014, Pelissier2013} have brought some methodological advances,
but are not sufficient for two reasons. First, these techniques are still
based on a `species-based' approach to communities, where interactions
are merely treated as fixed covariates affecting distribution. Second,
they failed to provide a conceptual step forward, both in their treatment
of interactions and in the quality of the predictions they make.

Because it is an explicit description of species interactions, the network
approach offers a convenient representation of communities. Species are
represented as nodes, so that networks already encompass all the information
used by current approaches; in addition, interactions are represented by links,
so that networks provide additional, higher-order information on community
structure. To date, studies of network diversity have mostly been concerned
with the distribution of interactions within locations, and less so with
the variation among locations \citep{Dunne2005, Bascompte2007, Ings2007,
Kefi2012}. There is however ample evidence that interaction networks vary
in space and time \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016,
Trojelsgaard2015}. Metacommunity theory provides explanations for the variation
in the distribution species \citep{Gravel2011c, Pillai2011}, but there is
no such explanation to the variation of node and link occurrences, nor do
we expect their distribution to covary in a positive way. Consequently,
we urgently need a conceptual framework to formalize these observations,
as it is the only way towards fulfilling the goal of community ecology:
providing cogent predictions about, and understanding of, the structure of
ecollogical communities.

@@

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|X_{iy},X_{jy},E_y)
\end{equation}
%-----------------

The first term on the right-hand side of the equation is the probability
of observing the two species co-occurring at location $y$. It corresponds
to the Grinnellian dimension of the niche. The second term represents the
probability that an interaction occurs between species $i$ and $j$, given that
they are co-occurring. This predicate can be refined using information on
trait distribution and trait matching rules (\textbf{Bartomeus Func Ecol}).
Above, we referred to this entity as the ``metaweb'' and it corresponds to
the Eltonian dimension of the niche. Below, we will see how this formalism
can be directly fit to empirical data. But before turning to an application,
we will discuss the interpretation of different variants of these two terms.
